 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - Cover Letter Template
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{John}{Doe}{ \urlstyle{same}\href{https://eeriksak.si}{eeriksak.si} | \href{mailto:saksi.eerik@gmail.com}{saksi.eerik@gmail.com} | +44 7519 698 702 | \urlstyle{same}\href{https://github.com/EerikSaksi}{Github} | \urlstyle{same}\href{https://fi.linkedin.com/in/eerik-saksi-b58324193}{Linkedin}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     MAIN COVER LETTER CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hfill

\begin{minipage}[t]{0.5\textwidth} 
\companyname{Morgan Stanley}
\companyaddress{
122 Waterloo St \\ 
Glasgow \\
G2 7DP 
}

\end{minipage}
\begin{minipage}[t]{0.49\textwidth} 
\currentdate{\today}
\end{minipage}

\lettercontent{Dear Recruiter,}

% The first paragraph of your job application letter should include information on why you are writing. Mention the job you are applying for and where you found the position. If you have a contact at the company, mention the person's name and your connection here.

\lettercontent{
    As a student at University of Glasgow, many of my colleagues have praised their internships at Morgan Stanley. Unlike the stories I heard from it's competitors, Morgan Stanley is using the top technology when it comes to cybersecurity, machine learning, automation, and user experience.}


   
% The next section of your cover letter should describe what you have to offer the company. Make strong connections between your abilities and the requirements listed in the job posting. Mention specifically how your skills and experience match the job. Expand on the information in your resume.
% Try to support each statement you make with a piece of evidence. Use several shorter paragraphs or bullets rather than one large block of text, which can be difficult to read and absorb quickly.
%For example 

% Using the knowledge and skills I have acquired in my <DEGREE PROGRAM> combined with my technical abilities I believe I can provide significant value to <COMPANY> while providing me invaluable experience to <PREPARE FOR OR FURTHER CAREER>.
% <RELEVANT LIFE STORY/ WORK/ PROJECT >
% In own projects, my coursework, work as a <PREVIOUS JOB TITLE> I have applied knowledge of <SUBJECT MATTER>.
% <LIST OF SMART SOUNDING SKILLS AND TOOLS>.
% Combining these tools with my interests in <FIELD> issues, I hope to help the <DEPARTMENT> answer questions about the <SUBJECT> behind <FIELD> projects.

\lettercontent{At my first job at UROS, I learned how satisfying solving a problem can feel. Conversly, I also learned how reverse engineering old software solutions was something that I wouldn't wish upon my worst enemy. Ever since then, I have been determined to learn the newest technologies and best practices in the hopes that I would never impose poor software solutions to future source code maintainers. I believe my passion for beautiful, expandable software solutions would make me a valuable addition to Morgan Stanley.  } 

\lettercontent{
 Along with the various technologies and languages I have learned to use at University of Glasgow, I have taught myself full stack development from scratch. I believe the web will be here to stay, and the rapid developments make it a challenging yet enticing field to specialize in. I believe both my acquired skills and my desire to learn will help me overcome any new and unfamiliar challenges I may encounter as a technology analyst at Morgan Stanley.}

% Conclude your application letter by thanking the employer for considering you for the position. 

\lettercontent{I thank you for taking the time to read my application and for considering me as a candidate for this position.}
\vspace{0.5cm}

\closing{Sincerely, 

Eerik Saksi
}


\end{document}  
\documentclass[]{article}
