\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{xcolor}
    \usepackage[hidelinks]{hyperref}


\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{scalerel}
\usepackage{stackengine}
\usepackage{pgf}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}
\hypersetup{
  colorlinks = true
}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}

\newcounter{iloop}
\newcommand\openbigstar[1][0.7]{%
  \scalerel*{%
    \stackinset{c}{-.125pt}{c}{}{\scalebox{#1}{\color{white}{$\bigstar$}}}{%
      $\bigstar$}%
  }{\bigstar}
}
\newcommand{\Stars}[1]{\ensuremath{%
\pgfmathtruncatemacro{\imax}{ifthenelse(int(#1)==#1,#1-1,#1)}%
\pgfmathsetmacro{\xrest}{0.9*(1-#1+\imax)}%
\setcounter{iloop}{0}%
\loop\stepcounter{iloop}\ifnum\value{iloop}<\the\numexpr\imax+1
\bigstar\repeat
\openbigstar[\xrest]%
\setcounter{iloop}{0}%
\loop\stepcounter{iloop}\ifnum\value{iloop}<\the\numexpr5-\imax\relax
\openbigstar[.9]\repeat}}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Eerik Saksi}}\\
  Helsinki, Finland $\cdot$ saksi.eerik@gmail.com $\cdot$ +44 7519 698 702 $\cdot$ \url{eeriksak.si}  \\
\end{center}

%==== Education ====%
\header{Education}
\textbf{University of Glasgow}\hfill Glasgow\\
    MSci Computing (2nd Year Entry) \hfill Sep 2018 - May 2022\\
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{UROS} \hfill Oulu, Finland\\
\textit{Software Engineer} \hfill June 2019 - August 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item I reverse engineered a project built with LabVIEW, a neural network written in C and an MYSQL database.
  \item I then replaced LabVIEW and the C library with a singular Python project that used the existing MYSQL database.
  \item UROS could then use more modern data processing without losing backwards compatibility with existing customer data.

\end{itemize}
\textbf{Leidos} \hfill Glasgow\\
\textit{Team project} \hfill November 2019 - March 2020\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Leidos wanted our 5 person team to help manage their parking at their company.
  \item I developed most the React Native app, aswell as helping my teammates use FastAPI.
\end{itemize}

\header{Skills}
\begin{tabular}{l p{0.1\textwidth} l}
  Javascript/Typescript & \Stars{4} & In both backend and frontend                                                           \\
  React  & \Stars{3}  & Material UI, React Router, Jest, React Bootstrap, Apollo Client etc. \\
	node.js & \Stars{3}               & Sequelize, Apollo Server, Jest, Express,    \\ 
  &  & node-fetch/node-html-parser, type-orm/type-graphql, PostGraphile \\
	SQL & \Stars{3}               & Postgres/SQLite and ORM\textquotesingle{}s (SQLAlchemy, Django ORM).          \\
  &  & Also studied Database Systems in Glasgow. \\
  Python & \Stars{3} & Scikit-learn, NumPy, pandas, Django, FastAPI, Flask. \\
  Shellscript & \Stars{3} & I develop in Linux, and constantly automate tasks with bash scripts.                                                           \\
  Java & \Stars{2}              & Java programming 2, all algorithms classes for code implementations, \\
  & & my primary language to practicing algorithm problems on Leetcode. \\ 
  C / C++  & \Stars{2}              & Reverse engineered and replaced C library at UROS, \\
  & & learned C and C++ in depth in Systems Programming.  \\ 
  Haskell & \Stars{1}              & Functional Programming in Glasgow. \\
  \end{tabular}
\vspace{2mm}

\header{Actual languages}
\begin{tabular}{ l p{0.1\textwidth} l}
  English  &  \Stars{5} & Studied in English almost my entire life. \\
  Finnish  &  \Stars{5} & Always speak Finnish at home and now live in Finland.                \\
  German & \Stars{3} & Have lived in Switzerland for many years, and have a 4/5 in AP German \\
\end{tabular}
\vspace{2mm}

\header{Projects}
    {\textbf{Tune Type}} {\sl Sequelize, node.js, Express, Apollo Server, GraphQL, Google Oauth, React, Bootstrap} \hfill \url{tunety.pe}\\
With tunetype, you can select a song and practice your typing speed to the lyrics and song live. You can also create synchronizations for songs that haven\textquotesingle{}t been synchronized yet. I used YouTube\textquotesingle{}s and Genius\textquotesingle{}s API for searching and metadata. Hosted on Heroku.\\
\vspace*{2mm}
    {\textbf{Collaborative Activity Tracker}} {\sl Expo, PostGraphile, Typescript, Postgres} \hfill \url{https://github.com/EerikSaksi/level_5_project}\\
As my level 4 project, I'm making a collaborative activity tracker, which should encourage users who are exercising together to be more motivated. It has RPG elements, where getting stronger and being consistent increases your characters and thus your teams damage per second, which allows you to progress to further stages.\\
\vspace*{2mm}
    {\textbf{vim-marks-overhaul}} {\sl Vimscript} \hfill \url{https://github.com/EerikSaksi/vim-marks-overhaul}\\
    I overrode a core feature of my text editor (Vim's marks) in order to speed up my workflow. I constantly try to streamline my workflow with other configs as well, which you can find  \href{https://github.com/EerikSaksi/dotfiles}{here}.  \\
\vspace*{2mm}
    {\textbf{FridgeGerald}} {\sl Django} \hfill \url{https://github.com/EerikSaksi/FridgeGerald}\\
FridgeGerald suggests recipes based on what ingredients you have, prioritising those soon to spoil.\\
\vspace*{2mm}

\ 
\end{document}
